Pervasive nitrous oxide undersaturation in U.S. lakes and reservoirs

### 2025-03-07 manuscript/manuscript_file.Rmd
Updates to manuscript files for more efficient knit

# vector of figure names
objs <- c("cond_effect_no3.tif",
          "figure1.png",
          "figure2.tiff",
          "n2oFluxAndEmissionRateVsContinuousArea.tiff",
          "n2oStarBySize.tiff",
          "SIfigure1.tiff"
          )

@@

# load files if they exist
for(i in 1:N){
  if(file.exists(f[[i]]))
    print("Good! Figure already created")
  else
    print(paste0("missing figure: ", f[[1]]))
 }

@@

![Figure 3. Estimated interactive effects of surface water temperature (A and B) and waterbody size (B and D) with NO~3~ levels on the N~2~O saturation ratio.  A) The relationship between N~2~O saturation and surface water temperature, dependent upon nitrate (NO~3~) level.  The five, ordered, categorical levels for NO~3~ correspond to concentration ($\mu$g N L^-1^) ranges in the observed data of 1) below detection, 2) $\geq$ 0.55 and \< 4.09, 3) $\geq$ 4.09 and \< 30.20, 4) $\geq$ 30.20 and \< 223.13, and 5) $\geq$ 223.13. B) The relationship between N~2~O saturation and NO~3~ level conditional on surface water temperature. The NO~3~ effect was estimated at 5 quantiles of the surface temperatures observed (10%, 25%, 50%, 75%, 90%). C) The relationship between N~2~O saturation and waterbody surface area (log-transformed hectares) conditional on NO~3~ level. D) The relationship between N~2~O saturation and NO~3~ level conditional on (log) waterbody surface area (5 quantiles).  Horizontal dashed lines in each panel reflect an N~2~O saturation value of one.](manuscript_figures/cond_effect_no3.tif)

>>>>

# vector of figure names
objs <- c("cond_effect_no3.tiff",
          "figure1.png",
          "figure2.tiff",
          "n2oFluxAndEmissionRateVsContinuousArea.tiff",
          "n2oStarBySize.tiff",
          "SIfigure1.tiff"
          )

@@

# load files if they exist
for(i in 1:N){
  if(file.exists(f[[i]]))
    print("Good! Figure already created")
  else
    print(paste0("missing figure: running manuscript_support.R ", f[[1]]))
    source("./manuscript/manuscript_support.R", local = knitr::knit_global())
 }

@@

![Figure 3. Estimated interactive effects of surface water temperature (A and B) and waterbody size (B and D) with NO~3~ levels on the N~2~O saturation ratio.  A) The relationship between N~2~O saturation and surface water temperature, dependent upon nitrate (NO~3~) level.  The five, ordered, categorical levels for NO~3~ correspond to concentration ($\mu$g N L^-1^) ranges in the observed data of 1) below detection, 2) $\geq$ 0.55 and \< 4.09, 3) $\geq$ 4.09 and \< 30.20, 4) $\geq$ 30.20 and \< 223.13, and 5) $\geq$ 223.13. B) The relationship between N~2~O saturation and NO~3~ level conditional on surface water temperature. The NO~3~ effect was estimated at 5 quantiles of the surface temperatures observed (10%, 25%, 50%, 75%, 90%). C) The relationship between N~2~O saturation and waterbody surface area (log-transformed hectares) conditional on NO~3~ level. D) The relationship between N~2~O saturation and NO~3~ level conditional on (log) waterbody surface area (5 quantiles).  Horizontal dashed lines in each panel reflect an N~2~O saturation value of one.](manuscript_figures/cond_effect_no3.tiff)
